Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-04-01 paper.tex
update

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition focus mainly on one single type of requirements. Therefore, we propose a general comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable trade-off in consideration of both sides. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model, where PSO optimise a queue of task-related services that is decoded into composition solutions. We compare the effectiveness of PSO-based method with one recent GP-based method using the proposed comprehensive quality model, and also compare the effectiveness of our proposed comprehensive quality model with one promising QoS model.

@@

\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composition service that accommodates customers' complex requirements. 
%This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.

Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions. The syntactic dimension is covered by the XML-based technologies, such as $WSDL$, $SOAP$. The semantic dimension enables a better collaboration through ontology-based semantics, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services. The second challenge is related to finding solutions with optimised QoS. This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.

Existing works on service composition focus mainly on addressing only one challenge above. In these works, huge efforts have been devoted to QoS-aware web service compositions given a pre-defined abstract workflow. This is generally considered as a \textit{semi-automated web service composition} approach \cite{parejo2008qos}. Generating composition plans automatically in discovering and selecting suitable web services is a NP-hard problem \cite{moghaddam2014service}. In the past few years, despite many QoS-aware web service composition works \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive} employ Evolutionary Computation (EC) techniques to automatically generate composition solutions, but few works have enabled an \textit{automatic semantic web service composition}, where both QoS and quality of semantic matchmaking are optimised simultaneously to achieve a desirable balance.

@@

 \item To propose a PSO-based service composition approach using the proposed comprehensive quality model. To do that, we aim to find a service candidate queue that can be decoded into a service composition with the near-optimal comprehensive quality.  
 \item To address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model, we first compare our PSO-based approach with one recent GP-based approach \cite{ma2015hybrid} using our proposed quality model, and then compare our proposed quality model with one widely used QoS model using our proposed PSO-based approach.
\end{enumerate}

\section{Related Work} \label{relatedWork}
Substantial works on web service composition focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS requirements for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.

Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures the semantic description of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services, where the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions. However, this evaluation approach does not guarantee an optimised QoS of composition solutions.

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a heuristic service composition method, named LOEM (Local Optimisation and Enumeration Method), where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS. EC techniques are used to automatically generate solutions with optimal QoS. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Genetic Programming (GP) are used by Yu et al. \cite{yu2013adaptive}, the optimal solutions are reached by penalising infeasible solutions using a fitness function. A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based individuals, which are transformed from DAGs. To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where DAG-based service composition representations employ Graph-based evolutionary operators. An indirect PSO-based approach was introduced in \cite{da2016particle}. An optimised queue is used as an indirect representation that is decoded into a DAG. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality.

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic that associated to the resources of web services. Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow. An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal section algorithm with an decoded planning graph, but this approach is only studied in some cases.

@@

Our goal is to develop a PSO-based approach for automatically generating good service compositions. Often, many different service compositions can meet a user request but differ significantly in terms of QoS and semantic matchmaking quality. For example, in the classical travel planning context, some component service must be employed to obtain a travel map. Suppose that two services can be considered for this purpose. One service $S$ can provide a street map at a price of 6.72. The other service $S'$ can provide a tourist map at a price of 16.87. Because in our context a tourist map is more desirable than a street map, $S'$ clearly enjoys better semantic matchmaking quality than $S$ but will have negative impact on the QoS of the service composition (i.e., the price is much higher). One can easily imagine that similar challenges frequently occur when looking for service compositions. Hence, a good balance between QoS and semantic matchmaking quality is called for. We therefore propose a general comprehensive quality model in considering semantic matchmaking quality and QoS simultaneously.

We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is the set of service inputs that are consumed by $S$, $O_{S}$ the set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ the set of non-functional attributes of $S$. The inputs in $I_{S}$ and the outputs in $O_{S}$ are concepts in an ontology $\mathcal{O}$. The attributes $t_S, c_S, r_S, a_S$ refer to the response time, cost, reliability, and availability of service $S$, respectively. These four QoS attributes are most commonly used \cite{zeng2003quality}. \textit{Response time} ($t_S$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received. \textit{Cost} ($c_S$) is the amount of money that a service requester has to pay for executing the service. \textit{Reliability} ($r_S$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0. Similarly, \textit{availability} ($a_S$) is the probability that a service is accessible.

A \emph{service repository} $\mathcal{SR}$ is a finite collection of services with a common ontology $\mathcal{O}$. A \emph{service request} (also called \emph{composition task}) over $\mathcal{SR}$ is a tuple $T=(I_{T}, O_{T})$ where $I_{T}$ is the set of task inputs, and $O_{T}$ the set of task outputs. The inputs in $I_{T}$ and the outputs in $O_{T}$ are concepts in the ontology $\mathcal{O}$.

A service composition is commonly represented as a \emph{directed acyclic graph} (DAG). It nodes correspond to the services in the composition. Two services $S$ and $S'$ are connected by an edge $e$ if some output of $S$ serves as input for $S'$. Apparently, such outputs and inputs must semantically match to ensure the correct execution of the service composition. 
%Moreover, the overall service inputs and outputs associated with the DAG must satisfy the composition requirements provided by users.
%To answer a request from a user a suitable service composition is sought. 
The mechanism to compose services relies on the semantic descriptions of inputs and outputs, which enables inputs of services to be matched by outputs of other services. The following \emph{matchmaking types} are often used to describe the level of a match \cite{paolucci2002semantic}: For concepts $a, b$ in $\mathcal{O}$ the \emph{matchmaking} returns $exact$ if $a$ and $b$ are equivalent ($a \equiv b$), $plugin$ if $a$ ia a sub-concept of $b$ ($a \sqsubseteq b$), $subsume$ if $a$ is a super-concept of $b$ ($a \sqsupseteq b$), and $fail$ if none of previous matchmaking types is returned.
%($a \perp b$)
In this paper we are only interested in robust compositions where only $exact$ and $plugin$ matches are considered, see \cite{lecue2009optimizing}. 
%
As argued in \cite{lecue2009optimizing} $plugin$ matches are less preferable than $exact$ matches due to the overheads associated with data processing. We suggest to consider the semantic similarity of concepts when comparing different plugin types. For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and a closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively.

@@

Given a service request $T=(I_T,O_T)$, we represent a service composition solution for $T$ with services $S_1,\ldots,S_n$  by a DAG $WG=(V,E)$ with node set $V=\{Start, S_1, S_2, \ldots, S_n, End\}$ and edge set $E = \{e_{1}, e_{2},... e_{m} \}$. $Start$ and $End$ are two special services defined as $Start = (\emptyset, I_T, \emptyset )$ and $End  = (O_T, \emptyset, \emptyset)$ that account for the input and output requirements given by the request. 
%Each edge $e$ between two services $S$ and $S'$ is associated with a set of incoming outputs produced by $S$ and a set of outgoing inputs consumed by $S'$.
Each edge $e$ from a service $S$ to a service $S'$ means that service $S$ produces an output $a\in O_S$ that is matched (exact or plugin) to an input $b\in I_{S'}$ to be consumed by service $S'$ in the composition. Based on the matchmaking type the \emph{semantic matchmaking quality} of edge $e$ can be defined as follows:

@@

The \emph{QoS} of the service composition can be obtained by aggregating the QoS values of the participating services. For a service composition with services $ S_1, S_2, ... S_n$ we obtain the reliabilitiy $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $P_j$ is a path of length $\ell_j$}\} \cite{da2015graphevol}.$$

@@

\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution can be defined as a weighted sum of the individual criteria:

\begin{equation}
\label{equation8}
Fitness = w_1 \hat{MT} + w_2 \hat{SIM} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent with $\sum_{k=1}^{6} w_k= 1$. The weights can be adjusted according to users' preferences. Herein, the individual criteria are normalized so that the QoS value falls within the range from 0 to 1 where 1 means the best value and 0 means the worst. For this purpose, we normalize $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using formula (\ref{equation9}). To simplify the presentation we also use the notation $(Q_1,Q_2,Q_3,Q_4,Q_5,Q_6) = (MT,SIM,A,R,T,C)$. $MT$ and $S$ have minimum value 0 and maximum value 1. The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all service candidates in the service repository $\mathcal{SR}$ using greedy search, for discussion see Section \ref{PSO_based_approach}.

@@

\section{Experiment Study}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach. To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. $(2)$ measure the effectiveness of our proposed comprehensive quality model for achieving desirable balance of semantic matchmaking quality and QoS. To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.

An augmented version of Web service challenge 2009 (WSC09) used in \cite{ma2015hybrid,da2016genetic} including QoS attributes is used for our experiment. WSC09 is a benchmark dataset consisting of five composition tasks. These tasks are associated with an increasing number of services, and concepts in ontologies.

@@

\section{Conclusion}\label{conclusion}
This work introduces a general comprehensive evaluation model for considering semantic matchmaking quality and QoS simultaneously. We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desirable trade-off of both quality aspects. In addtion, we compare one recent GP-approach with our PSO-based method to show our performance that results in finding more optimised solutions. Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.

>>>>

\begin{document}
\maketitle
\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major challenges faced by researchers, semantic matchmaking and Quality of Service (QoS) optimisation. Semantic matchmaking aims to discover interoperable web services that can interact with each other by their resources described semantically. QoS optimisation aims to optimise the non-functional requirements of service users, e.g., minimum cost, maximal reliability. To meet users' requirements, one often needs to consider both semantic matchmaking quality and QoS simultaneously. Existing works on web service composition focus mainly on one single type of requirements. Therefore, we propose a comprehensive quality model considering semantic matchmaking quality and QoS simultaneously with an aim of achieving a more desirable balance on both sides. Further more, we develop a PSO-based service composition approach with explicit support for the comprehensive model. We also conduct experiments to address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model.

%where PSO optimise a queue of task-related services that is decoded into composition solutions. We compare the effectiveness of PSO-based method with one recent GP-based method using the proposed comprehensive quality model, and also compare the effectiveness of our proposed comprehensive quality model with one promising QoS model.

@@

\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composite service that accommodates customers' complex requirements. 
%This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.

Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions. The syntactic dimension is covered by the XML-based technologies, such as $WSDL$, $SOAP$. The semantic dimension enables a better collaboration through ontology-based semantics, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services. The second challenge is related to QoS optimisation. This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.

Existing works on service composition focus mainly on addressing only one challenge above. In these works, huge efforts have been devoted to QoS-aware web service compositions assuming a pre-defined abstract workflow is given. This is generally considered as a \textit{semi-automated web service composition} approach \cite{parejo2008qos}. Generating composition plans automatically in discovering and selecting suitable web services is a NP-hard problem \cite{moghaddam2014service}. In the past few years, many approaches \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive} to QoS-aware web service composition employ Evolutionary Computation (EC) techniques to automatically generate composition solutions, but few works have enabled an \textit{automatic semantic web service composition}, where both QoS and quality of semantic matchmaking are optimised simultaneously to achieve a desirable balance on both sides.

@@

 \item To propose a PSO-based service composition approach using the proposed comprehensive quality model. To do that, we aim to find a service candidate queue that can be decoded into a service composition with the near-optimal comprehensive quality.  
 \item To address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model, we first compare our PSO-based approach with one recent GP-based approach \cite{ma2015hybrid} using our proposed quality model, and then compare our proposed quality model with one widely used QoS model using our proposed PSO-based approach.
\end{enumerate}
\section{Related Work} \label{relatedWork}
Substantial works on web service composition focus on either semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} or QoS-aware web service composition \cite{gupta2015optimization,ma2015hybrid,qi2010combining,da2016particle,da2015graphevol,yu2013adaptive}, However, only a few researchers address both semantic matchmaking quality and QoS for web service composition problems. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some attempts on service composition that considers both aspects.

Semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} captures the semantic descriptions of web services' parameters using some kind of logic (e.g., description logic) that ensuring the interoperability of web services. In these approach, the number of web services or length of a graph representation for web service composition is minimised to reach the optimised composition solutions. However, this evaluation approach does not guarantee an optimised QoS of composition solutions.

QoS-aware web service composition is studied using traditional approaches or Evolutionary Computation (EC) techniques for finding near-optimised solutions. Qi et al. \cite{qi2010combining} propose a local optimisation and enumeration method, where a small number of promising candidates related to each task are considered by local selection, and composition solutions are enumerated to reach the near optimal QoS. EC techniques are widely used to automatically generate solutions with optimal QoS. Gupta et al. \cite{gupta2015optimization} employ a modified Genetic Algorithm (GA) using a binary string as an individual, which demands to be decoded into composition solutions. Yu et al.  \cite{yu2013adaptive} use Genetic Programming (GP) for finding optimal solutions that are reached by penalising infeasible solutions using a fitness function. A hybrid approach employing a greedy search and GP is introduced in \cite{ma2015hybrid} to generate functionally correct tree-based individuals, which are transformed from \emph{directed acyclic graph}s (DAGs). To eliminating the transformation process, a promising GraphEvol is proposed in \cite{da2015graphevol}, where graph-based evolutionary operators are employed. An indirect PSO-based approach was introduced in \cite{da2016particle}. An service queue is used as an indirect representation that is decoded into a DAG. These QoS-aware approaches \cite{gupta2015optimization,qi2010combining,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} do not consider semantic matchmaking quality.

Only a few works \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} consider both semantic matchmaking quality and QoS simultaneously. Lecue et al. \cite{lecue2009optimizing} propose a semi-automated web service composition using GA to encode a given abstract service workflow, where the evaluation of semantic matchmaking quality requires a complete and formal definition of ontology using description logic that associated to the resources of web services. Another GA-based approach \cite{fanjiang2014semantic} utilise process description language to encode pre-stored cases-based workflows, where workable services are composed to complete this workflow. An automated immune-inspired web service composition approach \cite{pop2009immune} employs a clonal selection algorithm to proliferate decoded planning graphs, but this approach is only studied in some cases.

@@

Our goal is to develop a PSO-based approach for automatically generating good service compositions. Often, many different service compositions can meet a user request but differ significantly in terms of QoS and semantic matchmaking quality. For example, in the classical travel planning context, some component service must be employed to obtain a travel map. Suppose that two services can be considered for this purpose. One service $S$ can provide a street map at a price of 6.72. The other service $S'$ can provide a tourist map at a price of 16.87. Because in our context a tourist map is more desirable than a street map, $S'$ clearly enjoys better semantic matchmaking quality than $S$ but will have negative impact on the QoS of the service composition (i.e., the price is much higher). One can easily imagine that similar challenges frequently occur when looking for service compositions. Hence, a good balance between QoS and semantic matchmaking quality is called for. We therefore propose a comprehensive quality model in considering semantic matchmaking quality and QoS simultaneously.

We consider a \emph{semantic web service} (\emph{service}, for short) as a tuple $S = (I_{S}, O_{S}, QoS_S)$ where $I_{S}$ is the set of service inputs that are consumed by $S$, $O_{S}$ the set of service outputs that are produced by $S$, and $QoS_{S}=\{t_S, c_S, r_S, a_S\}$ the set of non-functional attributes of $S$. The inputs in $I_{S}$ and the outputs in $O_{S}$ are concept-related parameters with the concepts in an ontology $\mathcal{O}$. The attributes $t_S, c_S, r_S, a_S$ refer to the response time, cost, reliability, and availability of service $S$, respectively. These four QoS attributes are most commonly used \cite{zeng2003quality}.
% \textit{Response time} ($t_S$) measures the expected delay in seconds between the moment when a request is sent and the moment when the results are received. \textit{Cost} ($c_S$) is the amount of money that a service requester has to pay for executing the service. \textit{Reliability} ($r_S$) is the probability that a request is correctly responded within the maximum expected time frame, which is expressed as a number between 1 and 0. Similarly, \textit{availability} ($a_S$) is the probability that a service is accessible.

A \emph{service repository} $\mathcal{SR}$ is a finite collection of services with a common ontology $\mathcal{O}$. A \emph{service request} (also called \emph{composition task}) over $\mathcal{SR}$ is a tuple $T=(I_{T}, O_{T})$ where $I_{T}$ is the set of task inputs, and $O_{T}$ the set of task outputs. The inputs in $I_{T}$ and the outputs in $O_{T}$ are concept-related parameters with the concepts in the ontology $\mathcal{O}$.

A service composition is commonly represented as a DAG. It nodes correspond to the services in the composition. Two services $S$ and $S'$ are connected by an edge $e$ if some output of $S$ serves as input for $S'$. Apparently, such outputs and inputs must semantically match to ensure the correct execution of the service composition. 
%Moreover, the overall service inputs and outputs associated with the DAG must satisfy the composition requirements provided by users.
%To answer a request from a user a suitable service composition is sought. 
The mechanism to compose services relies on the semantic descriptions of inputs and outputs, which enables inputs of services to be matched by outputs of other services. The following \emph{matchmaking types} are often used to describe the level of a match \cite{paolucci2002semantic}: For concepts $a, b$ in $\mathcal{O}$ the \emph{matchmaking} returns $exact$ if $a$ and $b$ are equivalent ($a \equiv b$), $plugin$ if $a$ is a sub-concept of $b$ ($a \sqsubseteq b$), $subsume$ if $a$ is a super-concept of $b$ ($a \sqsupseteq b$), and $fail$ if none of previous matchmaking types is returned.
%($a \perp b$)
In this paper we are only interested in robust compositions where only $exact$ and $plugin$ matches are considered, see \cite{lecue2009optimizing}. 
%
As argued in \cite{lecue2009optimizing} $plugin$ matches are less preferable than $exact$ matches due to the overheads associated with data processing. We suggest to consider the semantic similarity of concepts when comparing different plugin types. For concepts $a, b$ in $\mathcal{O}$ the \emph{semantic similarity} $sim(a, b)$ is calculated based on the edge counting method defined in the formula (\ref{equation1}) from \cite{shet2012new}, where $N_a$, $N_b$ and $N_c$ measure the distances from concept $a$, concept $b$, and a closest common ancestor $c$ of $a$ and $b$ to the top concept of the ontology $\mathcal{O}$, respectively.

@@

Given a service request $T=(I_T,O_T)$, we represent a service composition solution for $T$ with services $S_1,\ldots,S_n$  by a weighted DAG, $WG=(V,E)$ with node set $V=\{Start, S_1, S_2, \ldots, S_n, End\}$ and edge set $E = \{e_{1}, e_{2},... e_{m} \}$. $Start$ and $End$ are two special services defined as $Start = (\emptyset, I_T, \emptyset )$ and $End  = (O_T, \emptyset, \emptyset)$ that account for the input and output requirements given by the request. 
%Each edge $e$ between two services $S$ and $S'$ is associated with a set of incoming outputs produced by $S$ and a set of outgoing inputs consumed by $S'$.
Each edge $e$ from a service $S$ to a service $S'$ means that service $S$ produces an output $a\in O_S$ that is matched ($exact$ or $plugin$) to an input $b\in I_{S'}$ to be consumed by service $S'$ in the composition. Based on the matchmaking type the \emph{semantic matchmaking quality} of edge $e$ can be defined as follows:

@@

The \emph{QoS} of the service composition can be obtained by aggregating the QoS values of the participating services. For a service composition with services $ S_1, S_2, ... S_n$ we obtain the reliabilitiy $R=\prod\limits^n_{k=1}r_{S_k}$, the availability $A=\prod\limits^n_{k=1}a_{S_k}$, the cost $C=\sum\limits^n_{k=1}c_{S_k}$, and the response time $T$ is the time of most time-consumption path in the composition, i.e., $$T = MAX \{\sum\limits^{\ell_j}_{k=1}t_{S_k} | \text{ $j\in\{1,\ldots,m\}$ and $P_j$ is a path of length $\ell_j$}\}.$$

@@

\noindent When multiple quality criteria are involved into decision making, then the overall fitness of a solution is evaluated by a proposed comprehensive quality model, which can be defined as a weighted sum of the individual criteria:

\begin{equation}
\label{equation8}
Fitness = w_1 \hat{MT} + w_2 \hat{SIM} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent with $\sum_{k=1}^{6} w_k= 1$. The weights can be adjusted according to users' preferences. Herein, the individual criteria are normalised to a range between 0 to 1, where 1 means the best value and 0 means the worst. For this purpose, we normalise $MT$, $SIM$, $A$, $R$, $T$, and $C$ so that the function value falls within the range from 0 to 1 using formula (\ref{equation9}). To simplify the presentation we also use the notation $(Q_1,Q_2,Q_3,Q_4,Q_5,Q_6) = (MT,SIM,A,R,T,C)$. $MT$ and $S$ have minimum value 0 and maximum value 1. The minimum and maximum value of $A$, $R$, $T$, and $C$ are calculated across all task-related candidates in the service repository $\mathcal{SR}$ using greedy search, for discussion see Section \ref{PSO_based_approach}.

@@

\section{Experiment Study}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design using an augmented version of Web service challenge 2009 including QoS attributes, which is used in \cite{ma2015hybrid,da2016genetic}. Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach. 
%To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. 
$(2)$ measure the effectiveness of our proposed comprehensive quality model for achieving desirable balance of semantic matchmaking quality and QoS. 
%To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.

%WSC09 is a benchmark dataset consisting of five composition tasks. These tasks are associated with an increasing number of services, and concepts in ontologies.

@@

\section{Conclusion}\label{conclusion}
This work introduces a comprehensive evaluation model for considering semantic matchmaking quality and QoS simultaneously. We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desirable trade-off of both quality aspects. In addtion, we compare one recent GP-approach with our PSO-based method to show our performance that results in finding more optimised solutions. Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.
